Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-07 Papers/ms.tex
Run details

>>>>

{\revisions As with the `easy' dataset,
we generated 5,000 samples from the DNS target distribution and thinned
by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
performed, taking approximately 60 hours. The slower runtime in this case
was because $N_{\rm lens} = 10$, more CPU time was spent exploring parts of
the hypothesis space where $N_{\rm lens}$ is high. The run resulted in 557
equally-weighted posterior samples.
}
